Geometric variational problems

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
broader impacts edited

The proposed mathematical analysis, modeling, and numerical algorithms
will transform our understanding of the collective dynamics of
amphiphilic particles such as (1) their self-assembly into micelles and
bilayers, (2) the material properties of such self-assembly, and (3) the
interaction between these building blocks. In addition to biophysical
applications, amphiphilic Janus particles have recent popularity in the
fabrication of smart materials. The proposed work will have a
transformative impact on precision design for specific mechanical
properties of materials made of amphiphilic nanoparticles. An important
component of this proposal is the interdisciplinary education and
training of both undergraduate students, graduate students, and
postdoctoral fellows. The combination of mathematical modeling,
analysis, and scientific computing in this project provides a compelling
example of the importance of mathematics in biophysics and engineering
applications. The concepts and methods described here go beyond the
context of amphiphilic particles and lipid molecules. They extend to
other problems featuring microscopic phase separation that leads to
formation of mesoscopic domains. This situation arises, for example, in
biological development in systems biology. The methods developed here
have the potential to impact those and other related areas in
biomedicine and biotechnology.

@@

The URs will work as a team for eight weeks in the summer. They will
collaborate directly with the senior personnel, have tutorials in topics
such as numerical quadrature and integral equations, and train in
mathematical writing and presentation. To maximize vertical integration,
and to the extent possible, the PIs and personnel will travel to 
New York for one or two weeks in the summers. Fordham University 
recently constructed a seminar/collaboration space specifically
for collaborative research, and URs will base there activitied from here.

@@

Innovations in teaching: we will create several modules to include
in our courses. These modules will introduce topics from numerical linear
algebra and optimization, and be based on the ideas of the proposal.
Additionally, we and our UR collaborators will give remote, guest lectures
in each others' courses and undergraduate seminars.

>>>>

The proposed mathematical analysis, modeling, and numerical algorithms
will transform our understanding of the collective dynamics of
amphiphilic particles such as (1) their self-assembly into micelles and
bilayers, (2) the material properties of such self-assembly, and (3) the
interaction between these building blocks. In addition to biophysical
applications, amphiphilic Janus particles have recent popularity in the
fabrication of smart materials. The proposed work will have a
transformative impact on precision design for specific mechanical
properties of materials made of amphiphilic nanoparticles. An important
component of this proposal is the interdisciplinary education and
training of both undergraduate students, graduate students, and
postdoctoral fellows. The combination of mathematical modeling,
analysis, and scientific computing in this project provides a compelling
example of the importance of mathematics and computation in biophysics
and engineering applications. The concepts and methods described here go
beyond the context of amphiphilic particles and lipid molecules. They
extend to other problems featuring microscopic phase separation that
leads to formation of mesoscopic domains. This situation arises, for
example, in biological development in systems biology. The methods
developed here have the potential to impact those and other related
areas in biomedicine and biotechnology.

@@

The URs will work as a team for eight weeks in the summer. They will
collaborate directly with the senior personnel, have tutorials in topics
such as numerical quadrature and integral equations, and train in
mathematical writing and presentation. To maximize vertical integration,
and to the extent possible, the PIs and personnel will travel to New
York for one or two weeks in the summers. Fordham University recently
constructed a seminar/collaboration space specifically for collaborative
research, and the URs will have office space with desks there.

@@

Finally, we will create several modules to include in our courses. These
modules will introduce topics from numerical linear algebra and
optimization, and be based on the ideas of the proposal. Additionally,
we and our UR collaborators will give remote, guest lectures in each
others' courses and undergraduate seminars.
